Supporting Information : Effect of copula on extinction risk

### 2019-02-27 SuppMat.Rmd
editing

  plot(ss$d,ss$risk_left,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  liness(s$d,ss$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
  #---------------------------------------------------
  ## Allow a second plot on the same graph
  #par(new=TRUE)

  #ylm2<-c(-0.2,0.6)
  ## Plot the second plot and put axis scale on right
  #plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
  #     axes=FALSE, type="l", col="orange")
 # abline(h=0,lty="dotted",col="grey")
 # lines(s$d, s$pop_avg_acf_right, col="skyblue")

@@

for(i in 1:dim(res_ricker_global)[3]){
  #s<-res_ricker_global
  ss<-res_ricker_global[,,i][1:6,] # plot for d in range (0 to 0.5)
  ss<-as.data.frame(ss)

>>>>

  plot(ss$d,ss$risk_left,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
  #---------------------------------------------------
  ## Allow a second plot on the same graph
  #par(new=TRUE)

  #ylm2<-c(-0.2,0.6)
  ## Plot the second plot and put axis scale on right
  #plot(ss$d, ss$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
  #     axes=FALSE, type="l", col="orange")
 # abline(h=0,lty="dotted",col="grey")
 # lines(ss$d, ss$pop_avg_acf_right, col="skyblue")

@@

for(i in 1:dim(res_ricker_global)[3]){
  #ss<-res_ricker_global
  ss<-res_ricker_global[,,i][1:6,] # plot for d in range (0 to 0.5)
  ss<-as.data.frame(ss)
